Self Regulation Ontology Retest Data Report

### 2017-04-14 SRO_Report.Rmd
added ddm distributions plot and failed effort to making it interactive

@@

@@

  for(i in 1:nrow(ref_df)){
    for(j in 1:nrow(plot_df)){
      if(ref_df[i, bin_col] <= plot_df$xmax[j] & ref_df[i, bin_col]>=plot_df$xmin[j] & ref_df[i, group_col] == plot_df[j, group_col]){
        ref_df$bin[i] <- plot_df$bin[j]
      }
    }
  }

  ref_df = ref_df %>% 
    group_by(bin, task) %>%
    mutate(label=as.character(toJSON(unique(dv))))

  label_df = ref_df[!duplicated(ref_df[,c('label')]),c('task', 'bin', 'label')]

  out_df = left_join(plot_df,label_df, by= c("bin", "task"))

@@

We aim to make contact with the literature to make the results more accesible to readers who have experience with our tasks but do not want to   
a. take away from the novelty of the main papers coming out of this project outlining the factor structure that this data unveils   
b. necessarily make prescriptive recommendations or theoretical arguments on why certain measures of certain processes are more reliable than others.

@@

- All parameters that were fit to all trials compared to contrasts have higher relialibilities.   
- Raw variables are not the variables with highest reliabilities overall.  
- 2 of 3 hddm parameters also have higher mean reliabilities than EZ parameter estimates.

@@

```{r warning=FALSE, message=FALSE}
tmp %>%
  select(dv, icc, spearman, label_1, label_2, label_3) %>%
  gather(key, value, -dv, -label_1, -label_2, -label_3) %>%
  ggplot(aes(value, color=label_2, fill=label_3))+
  geom_histogram(position='identity', alpha = 0.5)+
  theme_bw()+
  facet_wrap(key~label_1)+
  labs(color="Model", fill="Parameter")
```

>>>>

## Tasks

## Surveys

@@

## Data collection

@@

  for(i in 1:nrow(ref_df)){
    for(j in 1:nrow(plot_df)){
      if(ref_df[i, bin_col] <= plot_df$xmax[j] & ref_df[i, bin_col]>=plot_df$xmin[j] & all(ref_df[i, group_col] == plot_df[j, group_col])){
        ref_df$bin[i] <- plot_df$bin[j]
      }
    }
  }

  ref_df = ref_df %>% 
    group_by_("bin", group_col) %>%
    mutate(label=as.character(toJSON(unique(dv))))

  label_df = ref_df[!duplicated(ref_df[,c('label')]),c(group_col, 'bin', 'label')]

  out_df = left_join(plot_df,label_df, by= c("bin", group_col))

@@

We aim to make contact with the literature to make the results more accesible to readers who have experience with our tasks but do not want to   
1. take away from the novelty of the main papers coming out of this project outlining the factor structure that this data unveils   
2. necessarily make prescriptive recommendations or theoretical arguments on why certain measures of certain processes are more reliable than others.

@@

- All parameters that were fit to all trials compared to contrasts have higher relialibilities.   
- Raw variables are not the variables with highest ICC's overall. Raw response times do, however, have the highest Spearman's $\rho$'s on average. 
- 2 of 3 hddm parameters also have higher mean reliabilities than EZ parameter estimates.

@@

```{r warning=FALSE, message=FALSE}
tmp = tmp %>%
  select(dv, icc, spearman, label_1, label_2, label_3) %>%
  gather(key, value, -dv, -label_1, -label_2, -label_3)

tmp %>% ggplot(aes(value, color=label_2, fill=label_3))+
  geom_histogram(position='identity', alpha = 0.5)+
  theme_bw()+
  facet_wrap(key~label_1)+
  labs(color="Model", fill="Parameter")
```

```{r message=FALSE, echo=FALSE, eval=FALSE}
#attempt to make the above interactive. didn't really work
ggplotly(ggplot_build(tmp %>%
                        ggplot(aes(value, color=label_2, fill=label_3))+
                        geom_histogram(position='identity', alpha = 0.5)+
                        theme_bw()+
                        facet_wrap(key~label_1)+
                        labs(color="Model", fill="Parameter"))$data[[1]] %>%
           mutate(key = ifelse(PANEL %in%  c(1,2), "icc", "spearman"),
                  label_1 = ifelse(PANEL %in%  c(1,3), "all", "difference"),
                  label_2 = ifelse(colour == "#F8766D", "EZ", ifelse(colour == "#00BA38", "hddm", "raw")),
                  label_3 = ifelse(fill == "#A3A500", "drift rate", ifelse(fill == "#00BF7D", "non-decision", ifelse(fill == "#E76BF3", "threshold", ifelse(fill == "#F8766D", "accuracy", "rt"))))) %>%
           get_labels(.,tmp, "value", c("label_1", "label_2", "label_3", "key")) %>%
           prettify_label(.) %>%
           ggplot(aes(x, y, fill = label_3, color=label_2, label=label))+
           geom_bar(stat='identity',position='identity', alpha=0.5)+
           facet_wrap(key~label_1)+
           theme_bw(),
         tooltip = 'label',
         hoverinfo = 'text')
```
### Surveys
